---
output: 
  github_document:
    html_preview: false
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

reticulate::use_virtualenv("./env")
```

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Travis build status](https://travis-ci.org/news-r/gensimr.svg?branch=master)](https://travis-ci.org/news-r/gensimr)
<!-- badges: end -->

# gensimr

Brings [gensim](https://radimrehurek.com/gensim) to R.

## Installation

Install the package.

```r
install.packages("gensimr")
```

Install the python dependency. 

```r
gensimr::install_gensim()
```

Ideally one should use a virtual environment and pass it to `install_gensim`.

```r
system2("python3", "-m venv ./env") # create environment
reticulate::use_virtualenv("./env") # force reticulate to use env
gensimr::install_gensim("./env") # install gensim in environment
```

## Example

Use data from another [news-r](https://news-r.org) package.

Firdt we preprocess the corpus.

```{r}
library(gensimr)

docs <- preprocess(corpus)
```

Once preprocessed we can build a dictionary.

```{r}
dictionary <- corpora_dictionary(docs)
```

A dictionary essentially assigns an integer to each term.

```{r}
reticulate::py_to_r(dictionary$token2id)
```

`doc2bow` simply maps the `method of the same name to every documents; it counts the number of occurrences of each distinct word, converts the word to its integer word id and returns the result as a sparse vector. 

```{r}
# native method
dictionary$doc2bow(docs[[1]])

# apply to all documents
corpus <- doc2bow(dictionary, docs)
```

Then convert to matrix market format and serialise, the function returns the path to the file.

```r
(mm_corpus <- mmcorpus_serialize(corpus))
```

Then initialise a model.

```r
model <- model_tfidf(mm_corpus)
```

```r
corpus_transformed <- corpora_transform(model, corpus)
```

```r
lsi <- model_lsi(corpus_transformed, dictionary)
lsi$print_topics()

wrapped_corpus <- wrap_corpus(lsi, corpus_transformed)
wrapped_corpus_docs <- wrap_corpus_docs(wrapped_corpus)
```