---
title: "Topic Coherence"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Topic Coherence}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

reticulate::use_virtualenv("../env", required = TRUE)
```

This is a reproduction of the official tutorial on [Topic coherence](https://github.com/RaRe-Technologies/gensim/blob/develop/docs/notebooks/topic_coherence_tutorial.ipynb).

We will be using the `u_mass` and `c_v` coherence for two different LDA models: a "good" and a "bad" LDA model. The good LDA model will be trained over 50 iterations and the bad one for 1 iteration. Hence in theory, the good LDA model will be able come up with better or more human-understandable topics. Therefore the coherence measure output for the good LDA model should be more (better) than that for the bad LDA model. This is because, simply, the good LDA model usually comes up with better topics that are more human interpretable.

## Preprocess

As stated in table 2 from [this paper](http://www.cs.bham.ac.uk/~pxt/IDA/lsa_ind.pdf), this corpus essentially has two classes of documents. First five are about human-computer interaction and the other four are about graphs. We will be setting up two LDA models. One with 50 iterations of training and the other with just 1. Hence the one with 50 iterations ("better" model) should be able to capture this underlying pattern of the corpus better than the "bad" LDA model. Therefore, in theory, our topic coherence for the good LDA model should be greater than the one for the bad LDA model.

```{r}
library(gensimr)

data("corpus", package = "gensimr")

texts <- prepare_documents(corpus)
dictionary <- corpora_dictionary(texts)
corpus_bow <- doc2bow(dictionary, texts)

tfidf <- model_tfidf(corpus_bow, id2word = dictionary)
corpus_tfidf <- wrap(tfidf, corpus_bow)
```

## Set up two topic models

We'll be setting up two different LDA Topic models. A good one and bad one. To build a "good" topic model, we'll simply train it using more iterations than the bad one. Therefore the u_mass coherence should in theory be better for the good model than the bad one since it would be producing more "human-interpretable" topics.

```{r}
good_lda_model <- model_lda(corpus = corpus_tfidf, id2word = dictionary, iterations = 50L, num_topics = 2L)
bad_lda_model <- model_lda(corpus = corpus_tfidf, id2word = dictionary, iterations = 1L, num_topics = 10L)
```

## Interpreting the topics

As we will see below using LDA visualization, the better model comes up with two topics composed of the following words:

__good\_lda\_model:__

- Topic 1: More weightage assigned to words such as "system", "user", "eps", "interface" etc which captures the first set of documents.
- Topic 2: More weightage assigned to words such as "graph", "trees", "survey" which captures the topic in the second set of documents.

__bad\_lda\_model:__

- Topic 1: More weightage assigned to words such as "system", "user", "trees", "graph" which doesn't make the topic clear enough.
- Topic 2: More weightage assigned to words such as "system", "trees", "graph", "user" which is similar to the first topic. Hence both topics are not human-interpretable.

Therefore, the topic coherence for the `good\_lda\_model` should be greater for this than the `bad\_lda\_model` since the topics it comes up with are more human-interpretable. We will see this using `u_mass` and `c_v` topic coherence measures.

## U_Mass Coherence

```{r}
good_cm <- model_coherence(model = good_lda_model, corpus = corpus_tfidf, dictionary = dictionary, coherence = 'u_mass')
bad_cm <- model_coherence(model = bad_lda_model, corpus = corpus_tfidf, dictionary = dictionary, coherence = 'u_mass')
```

```{r}
good_cm$get_coherence()
bad_cm$get_coherence()
```

## Visualise

From the R console once can use the `plot` function to interactively open the visualisation.

```r
vis <- prepare_ldavis(good_lda_model, corpus, dictionary)
# plot(vis)
save_ldavis_html(vis, "lda.html")
htmltools::includeHTML("lda.html")
```

```{r, echo=FALSE}
htmltools::includeHTML("lda.html")
```

```{r}
good_cm$get_coherence()
bad_cm$get_coherence()
```

## Using C_V coherence

```{r}
good_cm <- model_coherence(model = good_lda_model, texts = texts, dictionary = dictionary, coherence = 'c_v')
bad_cm <- model_coherence(model = bad_lda_model, texts = texts, dictionary = dictionary, coherence = 'c_v')
```

```{r}
good_cm$get_coherence()
bad_cm$get_coherence()
```

Hence as we can see, the `u_mass` and `c_v` coherence for the good LDA model is much more (better) than that for the bad LDA model. This is because, simply, the good LDA model usually comes up with better topics that are more human interpretable. The `bad_lda_model` however fails to decipher between these two topics and comes up with topics which are not clear to a human. The `u_mass` and `c_v` topic coherences capture this wonderfully by giving the interpretability of these topics a number as we can see above. Hence this coherence measure can be used to compare difference topic models based on their human-interpretability.

## Map

You can also apply the `model_coherence` to multiple models at once using `map_coherence`.

```{r}
# create a model collection
models <- list(good_lda_model, bad_lda_model)
(model_collection <- as_model_collection(models))

# compute topic coherence
model_collection <- map_coherence(model_collection, corpus = corpus_tfidf, dictionary = dictionary, coherence = 'u_mass')
get_coherence_data(model_collection)
```

## Workflow

In the real world you will likely use the `map_*` functions to run and assess multiple models at once then assess which is best using the perplexity score. Here we use the `reuters` dataset from the [textanalysis package](https://textanalysis.news-r.org/) as a larger corpus helps to better demonstrate. The `reuters` package is a set of reuters articles on 10 different commodities.

```{r}
# remotes::install_github("news-r/textanalysis")
data("reuters", package = "textanalysis")

# preprocess the reuters dataset
texts <- prepare_documents(reuters$text)
dictionary <- corpora_dictionary(texts)
corpus_bow <- doc2bow(dictionary, texts)

tfidf <- model_tfidf(corpus_bow, id2word = dictionary)
corpus_tfidf <- wrap(tfidf, corpus_bow)

# train multiple models
models <- map_model(
  corpus = corpus_tfidf, 
  id2word = dictionary
) 

# compute topic coherence of all models
models <- map_coherence(models, corpus = corpus_tfidf, dictionary = dictionary, coherence = 'u_mass')

get_coherence_data(models)

plot(models)
```

Coherence closer to 0 is better.