---
title: "Preprocessing"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Preprocessing}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

reticulate::use_virtualenv("./env")
```

First we preprocess the corpus using example data, a tiny corpus of 9 documents. Reproducing the tutorial on [corpora and vector spaces](https://radimrehurek.com/gensim/tut1.html).

```{r}
library(gensimr)

set.seed(42) # rerproducability

# sample data
data(corpus, package = "gensimr")
print(corpus)

# preprocess corpus
docs <- prepare_documents(corpus)
```

This produces the same output as the built-in prepared documents.

```{r}
common_texts()
```

## Preprocess

The following are methods that work on lists, character vectors and data.frames. The function `preprocess` applies all methods below (by default).

```{r}
preprocess(corpus)
```

## Remove Stopwords

Remove stopwords.

```{r}
remove_stopwords(corpus[[1]])
```

## Strip Short

Remove short words.

```{r}
remove_stopwords(corpus[[2]], min_len = 3)
```

## Split Alphanumerics

```{r}
split_alphanum("24.0hours7 days365 a1b2c3")
```

## Strip Punctuation

Replaces punctuation with space.

```{r}
strip_punctuation("A semicolon is a stronger break than a comma, but not as much as a full stop!")
```

## Strip Tags

Removes tags.

```{r}
strip_tags("<i>Hello</i> <b>World</b>!")
```

## Strip Numerics

Removes digits.

```{r}
strip_numerics("0text24gensim365test")
```

## Stem

Transform to lowercase and stem.

```{r}
stem_text("It is useful to be able to search a large collection of documents almost instantly.")
```

## Porter Stemmer

```{r}
stemmer <- porter_stemmer()
stemmer$stem_sentence("Cats and ponies have meeting")
stemmer$stem_documents(c("Cats and ponies", "have meeting"))
```