---
title: "Document Similarity"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Document Similarity}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

reticulate::use_virtualenv("../env")
```

Reproducing [tutorial on similarity](https://radimrehurek.com/gensim/tut3.html#similarity-interface).

## Preprocess

First preprocess the corpus.

```{r}
library(gensimr)

set.seed(42) # rerproducability

# sample data
data(corpus, package = "gensimr")
print(corpus)

# preprocess corpus
docs <- prepare_documents(corpus)

docs[[1]] # print first preprocessed document 
```

Once preprocessed we can build a dictionary.

```{r}
dictionary <- corpora_dictionary(docs)
```

A dictionary essentially assigns an integer to each term.

`doc2bow` simply applies the method of the same name to every documents (see example below); it counts the number of occurrences of each distinct word, converts the word to its integer word id and returns the result as a sparse vector. 

```{r}
# native method to a single document
dictionary$doc2bow(docs[[1]])

# apply to all documents
corpus_bow <- doc2bow(dictionary, docs)
```

Then serialise to matrix market format, the function returns the path to the file (this is saved on disk for efficiency), if no path is passed then a temp file is created. Here we set `auto_delete` to `FALSE` otherwise the corpus is deleted after first use. Note this means you should manually delete it with `delete_mmcorpus`.

```{r}
(corpus_mm <- serialize_mmcorpus(corpus_bow, auto_delete = FALSE))
```

Then initialise a model, we're going to use a Latent Similarity Indexing method later on (`model_lsi`) which requires td-idf.

```{r}
tfidf <- model_tfidf(corpus_mm)
```

We can then use the model to transform our original corpus.

```{r}
corpus_transformed <- wrap(tfidf, corpus_bow)
```

## One Document

Now we can compare similarity between our preprocessed corpus and a new document.

```{r}
lsi <- model_lsi(corpus_transformed, id2word = dictionary)

mm <- read_serialized_mmcorpus(corpus_mm)

new_document <- "A human and computer interaction"
preprocessed_new_document <- preprocess(new_document, min_freq = 0)
vec_bow <- doc2bow(dictionary, preprocessed_new_document)
vec_lsi <- wrap(lsi, vec_bow)

wrapped_lsi <- wrap(lsi, mm)
index <- similarity_matrix(wrapped_lsi)

sims <- wrap(index, vec_lsi)

get_similarity(sims)
```

## Matrix

You can also compare documents in the corpora with one another. The method is slightly different to improve computational efficiency. Note that we set the number of features to the number of words in the dictionary.

The visualisation (matrix of cosine similarities) reveals the two clusters of documents again: as stated in table 2 from [this paper](http://www.cs.bham.ac.uk/~pxt/IDA/lsa_ind.pdf), the example corpus (`data(corpus)`) essentially has two classes of documents. First five are about human-computer interaction and the other four are about graphs. 

```{r}
# build model
index2 <- similarity(corpus_mm, num_features = reticulate::py_len(dictionary))

# query all similarities
sims <- wrap(index2, corpus_bow, to_r = TRUE)

sims_long <- reshape2::melt(sims)

library(ggplot2)

sims_long %>% 
  dplyr::mutate_at(dplyr::vars(c("Var1", "Var2")), as.factor) %>% 
  ggplot(aes(Var1, Var2)) + 
  geom_tile(aes(fill = value)) + 
  theme(
    panel.background = element_rect(fill = "#f4f1e6"),
    plot.background = element_rect(fill = "#f4f1e6"),
    legend.background = element_rect(fill = "#f4f1e6")
  ) +
  xlab("Document") +
  ylab("Document") 
```

Clean up, delete the corpus.

```{r}
delete_mmcorpus(corpus_mm)
```